Dynein walks like an Imperial AT-ST

### 2018-05-31 papers/paper/paper.tex
Add initial work on dynamic model+cryoem micrograph figure

\begin{figure}[tbhp]
\centering
\includegraphics[width=0.49\linewidth]{figures/onebound-cartoon.pdf}
\includegraphics[width=0.49\linewidth]{figures/bothbound-cartoon.pdf}
\caption{Cartoon representation of model systems. \textbf{Left}: Post-powerstroke, \textbf{right}: pre-powerstroke.}
\label{fig:duration-length}
\end{figure}

@@

>>>>

\begin{figure*}[tbhp]
\centering
\includegraphics[width=0.3\linewidth]{figures/onebound-cartoon.pdf}%
\includegraphics[width=0.3\linewidth]{figures/bothbound-cartoon.pdf}%
\includegraphics[width=0.3\linewidth]{figures/schematic-1-superimposed}\\
\includegraphics[width=0.15\linewidth]{../../plots/poststroke-figure.pdf}%
\includegraphics[width=0.15\linewidth]{../../plots/prestroke-figure.pdf}%
\includegraphics[width=0.3\linewidth]{figures/schematic-binding-angle}
\caption{}
\label{fig:duration-length}
\end{figure*}

@@

\section{To do items}

\subsection{Elliott}
\begin{enumerate}
\item Document carefully where all figures and data comes from.
\item Make our cool figures presentable, e.g. trajectory plot.
\item Describe our algorithm in sufficient detail.
\item Ensure our experimental figures have at least one version with
  scale bars.
\item Write script to generate figures with cartoon on top of
  microscopy images.
\item Store our preferred geometric (and non-geometric) parameters in
  a python module, which is used both for creating figures (see above)
  and for running simulations.
\item Python script to write out latex with parameters.
\item Fix stepping analysis python module to categorize zero-length
  steps separately from other steps, particularly in terms of stepping
  times.  Alternately, change C++ to make it possible to identify
  which foot lifted if it didn't move.
\item Update plotting scripts to use stepping analysis python module,
  or other modules.
\item Write up how we estimate one-bound/bothbound time ratio from
  processivity.  Ensure simulation obeys this?
\item Keep trying to get data from Yildiz.
\end{enumerate}

\subsection{John}
\begin{enumerate}
\item Proofread the algorithm description, improve its writing, and
  check against code.
\item Figure out how to do no-unbinding simulations to get Yildiz
  comparison data.  Also this gives us unbinding rates that will agree
  with our stepping time, etc. \verb!src/simulate_unbinding_rates.cpp!
\item Play with parameters to get stepping length histogram more
  reasonable (this automatically gives us the velocity).
\item Run long/many simulations with final parameters.
\item Run a low-ATP simulation for comparison data.
\item Nice final version of stepping length histogram.
\item Nice final version of tension-gating Yildiz comparison.
\item Consider a no-binding simulation and a separable model.  Create
  a figure demonstrating/testing whether the histogram of final
  displacement is independent of initial displacement.
\item Consider a simple Monte Carlo that just uses our no-unbinding
  and no-binding simulations to model dynein (like Yildiz).
\end{enumerate}

\section{Papers we should cite}
This paper says something interesting~\cite{leschziner}.
